Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-28 cbm-rbd-paper.tex
changes after dicussion with SDF

\subsection{System reliability function at $\tnow$}
\label{sec:sysreltnow}

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system reliability distribution $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
               \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Note that if one or several components have failed by $\tnow$,
the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
so we denote the updated survival signature by $\Phinow(l_1,\ldots,l_K)$.

@@

Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / (\tsysnow - \tnow) & \text{if } \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a time span starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] \nonumber\\ 
            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
\label{eq:gtnowtau}
\end{align}
and $\tausnow = \arg\min \gnow(\tau)$.
Thus $\tausnow$, the optimal moment of maintenance as of $\tnow$,
incorporates all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
Figure~\ref{fig:ghist1fig2} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
in a numeric example which is described in more detail in Section~\ref{sec:examples}.
%illustrates the derivation of $\tausnow$ .

@@

Note that for the integral in \eqref{eq:gtnowtau} to exist,
%$\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
$\E[1/(\Tsysnow - \tnow)]$ must exist,
which is a condition for $\fsysnow(\tnow + t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively
(see Section~\ref{sec:optim} below).

@@

For our choice of component model,
the resulting $\Rsysnow(t)$ as of \eqref{eq:sysrel-tnow}
is closed-form, but not tractable analytically.
Therefore,
we evaluate $\Rsysnow(t)$ on a dense grid of time points $t$
covering the time span from $\tnow$ to some horizon time $\tnow + t_h$.
(The choice of $t_h$ is discussed in more detail below.)
We calculate $\gnow(\tau)$ on the same grid,
and determine $\tausnow$ by minimizing over this grid.
Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
where evaluations of $\fsysnow(\tnow + t)$ are calculated via differences of $\Rsysnow(\tnow + t)$ evaluations.
%$\gnow(\tau)$ is likewise evaluated on a dense grid,
%and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.

The horizon time span $t_h$ can be determined by practical considerations,
but generally should reach far enough into the tail of $\Rsysnow(t)$
such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
Note that according to \eqref{eq:gtnowtau},
the calculation of $\gnow(\tau)$ requires
evaluations of $\Rsysnow(\tnow + t)$ and $\fsysnow(\tnow + t)$ only for $t \leq \tau$.

We have implememted our method in \textsf{R} \citep{R},
using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
to calculate survival signatures.
As the parameter update step is closed-form,
recalculation of $\tausnow$ is a matter of seconds,
allowing for a near real-time update.

>>>>

\subsection{Conditional system reliability function at $\tnow$}
\label{sec:sysreltnow}

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system reliability distribution $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
               \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Since this is the system reliability distribution conditional on the system surviving until $\tnow$,
we have that $\Rsysnow(\tnow) = 1$.
Note that if one or several components have failed by $\tnow$,
the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
so we denote the updated survival signature by $\Phinow(l_1,\ldots,l_K)$.

@@

Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / (\tsysnow - \tnow) & \text{if } \tnow < \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a time span starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] \nonumber\\ 
            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{\theta} \fsysnow(\tnow + \theta) \dd \theta\,,
\label{eq:gtnowtau}
\end{align}
and $\tausnow = \arg\min \gnow(\tau)$.
Thus $\tausnow$, the optimal moment of maintenance as of $\tnow$,
incorporates all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
Figure~\ref{fig:ghist1fig2} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
in a numeric example which is described in more detail in Section~\ref{sec:examples}.
%illustrates the derivation of $\tausnow$ .

@@

Note that for the integral in \eqref{eq:gtnowtau} to exist,
%$\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
$\E[1/(\Tsysnow - \tnow)]$ must exist,
which is a condition for $\fsysnow(\tnow + \theta)$ for values of $\theta$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively
(see Section~\ref{sec:optim} below).

@@

For our choice of component model,
the resulting $\Rsysnow(t)$ as of \eqref{eq:sysrel-tnow}
is closed-form, but not tractable analytically.
Therefore,
we evaluate $\Rsysnow(t)$ on a dense grid of time points $t$
covering the time span from $\tnow$ to some horizon time $\tnow + t_h$.
(The choice of $t_h$ is discussed in more detail below.)
We calculate $\gnow(\tau)$ on the same grid,
and determine $\tausnow$ by minimizing over this grid.
Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
where evaluations of $\fsysnow(t)$ are calculated via differences of $\Rsysnow(t)$ evaluations.
%$\gnow(\tau)$ is likewise evaluated on a dense grid,
%and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.

The horizon time span $t_h$ can be determined by practical considerations,
but generally should reach far enough into the tail of $\Rsysnow(t)$
such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
Note that according to \eqref{eq:gtnowtau},
the calculation of $\gnow(\tau)$ requires
evaluations of $\Rsysnow(t)$ and $\fsysnow(t)$ only for $\tnow < t \le \tnow + \tau$.

We have implememted our method in \textsf{R} \citep{R},
using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
to calculate survival signatures.
As the parameter update step is closed-form,
recalculation of $\tausnow$ is a matter of one or two seconds,
allowing for a near real-time update.
